Bird beak's elaboration and exploration

### 2021-08-27 Analysis/02-MCMCglmm_mini_chains.Rmd
Ready for compute!

```{r load_beer, eval = TRUE, message = FALSE}
set.seed(42)
## Loading beer
library(beer)
library(MCMCglmm)

## Loading the demo data
data(demo_data)
data(demo_trees)
data(demo_tree)

## Setting the consensus tree
consensus_tree <- demo_tree
```

@@

```{r, parametrise_the_model, eval = TRUE}
## Set up the parametrising chains models
param_MCMCglmm <- make.mini.chains(data         = demo_data,
                                   dimensions   = c(1:4),
                                   tree         = consensus_tree,
                                   trait.family = "gaussian",
                                   randoms      = c("global", "clade"),
                                   residuals    = "global",
                                   priors       = 0.02,
                                   verbose      = TRUE,
                                   parameters   = list(
                                       nitt   = 10000,
                                       thin   = 100,
                                       burnin = 0))

## Running the three MCMCglmm models
param_chains <- run.mini.chains(param_MCMCglmm, replicates = 3)
```

@@

```{r, get_model_parameters, eval = TRUE}
## Extract the parameters from the parameter chains
est_params <- extract.parameters(param_chains)
```

@@

```{r, set_the_mini_chains, eval = TRUE}
## The thinning parameter
thin <- 100
## The number of samples per chains
samples <- 100

>>>>

```{r load_beer, eval = TRUE, message = FALSE}
set.seed(42)
## Loading beer
library(beer)
library(MCMCglmm)
library(dispRity)

## Loading the parametrisation data
load(file = "../Data/Processed/form_shape_space_1tree_2levels.rda")
```

@@

```{r, parametrise_the_model, eval = TRUE}
## Select the data
shapespace <- form_shape_space_1tree_2levels$shape_space
groups_list <- form_shape_space_1tree_2levels$groups_list
selected_dim <- form_shape_space_1tree_2levels$shape_dim
consensus_tree <- form_shape_space_1tree_2levels$consensus_tree

## Set up the parametrising chains models
param_MCMCglmm <- make.mini.chains(data         = shapespace,
                                   dimensions   = selected_dim,
                                   tree         = consensus_tree,
                                   trait.family = "gaussian",
                                   randoms      = c("global", "level1", "level2"),
                                   residuals    = "global",
                                   priors       = 0.02,
                                   verbose      = TRUE,
                                   parameters   = list(
                                       nitt   = 1000000,
                                       thin   = 500,
                                       burnin = 0))

## Running the three MCMCglmm models
params_shapespace_8D_31levels <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(param_chains, file = "../Data/Processed/MCMCglmm/params_shapespace_8D_31levels_chain1.rda")
```

@@

```{r, get_model_parameters, eval = FALSE}
## Extract the parameters from the parameter chains
est_params <- extract.parameters(param_chains)
```

@@

```{r, set_the_mini_chains, eval = FALSE}
## The thinning parameter
thin <- 100
## The number of samples per chains
samples <- 100
